### 2019-09-14 scache/tii/tex/impl.tex
Remove blue words

\section{Implementation}\label{impl}
This section presents an overview of the implementation of SCache. 
We first present the system overview and the detail of sampling in Subsection \ref{arch}. 
The following \ref{memorymanage} subsection focuses on two constraints on memory management.
% In Subsection \ref{crossframework}, we evaluate the cross-framework capability of SCache. 
% At last, we discuss the cost of adapting SCache and fault tolerance. 
{\color{blue}
In Subsection \ref{fault}, we discuss the fault tolerance of the system.
}

\subsection{System Overview}\label{arch}
{\color{blue}
As shown in Figure \ref{fig:architecture}, SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a worker daemon.
As a plug-in system, SCache needs to rely on a DAG framework. 
The master node of SCache includes a DAG co-scheduler and a storage manager.
The DAG co-scheduler is responsible for pre-scheduling the reduce tasks assignment and then forcing the DAG framework to assign reduce tasks according to this assignment.
The storage manager is used for managing the shuffle blocks saved in worker nodes.
% The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
% The coordination provides two guarantees: (a) data is stored in memory before tasks start and (b) data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
% The daemon bridges the communication between DAG framework and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to the original scheduler in framework.

@@

\subsection{Memory Management}\label{memorymanage}
% As mentioned in Section \ref{observation}, though the shuffle size is relatively small, memory management should still be cautious enough to limit the effect of performance of DAG framework.
{\color{blue}
SCache uses bellowed memory management to ensure performance.
If the reserved memory is running out, SCache will flush some of the blocks into the disk temporarily and then re-fetch them if needed.
SCache leverages two constraints to manage the shuffle blocks: \textit{all-or-nothing} and \textit{context-aware-priority}.
% When the size of cached blocks reaches the limit of reserved memory, SCache flushes some of them to the disk temporarily, and re-fetches them when some cached shuffle blocks are consumed or pre-fetched. 
% To achieve the maximum overall improvement, SCache leverages two constraints to manage the in-memory data --- \textit{all-or-nothing} and \textit{context-aware-priority}.
}

\subsubsection{All-or-Nothing Constraint}
% This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
{\color{blue}
% Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks.
% Both experience and DAG framework manuals (e.g., Hadoop and Spark) recommend that multi-round execution of each stage will benefit the performance of applications.
As discussed in the observation in Subsection \ref{observation}, it is common to have multi-round execution of each stage. 
If one of the tasks in a round missed a memory cache, the re-fetch overhead will become a bottleneck and then slow down the whole stage. 
% If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 
% PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously. 
% Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least.
}
Therefore, SCache master sets blocks of one round as the minimum unit of storage management.
We refer to this as the all-or-nothing constraint.
% According to all-or-nothing constraint, SCache master leverages the pre-scheduled results to determine the bound of each round, and sets blocks of one round as the minimum unit of storage management.
% For those incomplete units, SCache marks them as the lowest priority.

@@

{\color{blue}
\subsection{Discussion of Fault Tolerance}\label{fault}
% how to handle faults? -> maybe replication -> tradeoff
For now, SCache only restarts failed workers without recovering their data.
SCache leaves the fault handling to the DAG frameworks.
If a failure happens in a SCache worker during shuffle phases, the $getBlock$ API will return a data not found error which causes the DAG framework restarts the current stage.
During the re-computing, the DAG frameworks still use SCache to gain shuffle optimization.
A possible way to avoid this re-computing is to use replications to recover the data.
However, such replications can introduce a significant network overhead.
We believe that the current way is more promising because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as the paralleled recovery of Spark. 
% Meanwhile, SCache can still provide shuffle optimization during the re-computing.
}

>>>>

\section{Implementation}\label{impl}
This section presents an overview of the implementation of SCache. 
We first present the system overview and the detail of sampling in Subsection \ref{arch}. 
The following \ref{memorymanage} subsection focuses on two constraints on memory management.
% In Subsection \ref{crossframework}, we evaluate the cross-framework capability of SCache. 
% At last, we discuss the cost of adapting SCache and fault tolerance. 
{\color{black}
In Subsection \ref{fault}, we discuss the fault tolerance of the system.
}

\subsection{System Overview}\label{arch}
{\color{black}
As shown in Figure \ref{fig:architecture}, SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a worker daemon.
As a plug-in system, SCache needs to rely on a DAG framework. 
The master node of SCache includes a DAG co-scheduler and a storage manager.
The DAG co-scheduler is responsible for pre-scheduling the reduce tasks assignment and then forcing the DAG framework to assign reduce tasks according to this assignment.
The storage manager is used for managing the shuffle blocks saved in worker nodes.
% The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
% The coordination provides two guarantees: (a) data is stored in memory before tasks start and (b) data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
% The daemon bridges the communication between DAG framework and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to the original scheduler in framework.

@@

\subsection{Memory Management}\label{memorymanage}
% As mentioned in Section \ref{observation}, though the shuffle size is relatively small, memory management should still be cautious enough to limit the effect of performance of DAG framework.
{\color{black}
SCache uses bellowed memory management to ensure performance.
If the reserved memory is running out, SCache will flush some of the blocks into the disk temporarily and then re-fetch them if needed.
SCache leverages two constraints to manage the shuffle blocks: \textit{all-or-nothing} and \textit{context-aware-priority}.
% When the size of cached blocks reaches the limit of reserved memory, SCache flushes some of them to the disk temporarily, and re-fetches them when some cached shuffle blocks are consumed or pre-fetched. 
% To achieve the maximum overall improvement, SCache leverages two constraints to manage the in-memory data --- \textit{all-or-nothing} and \textit{context-aware-priority}.
}

\subsubsection{All-or-Nothing Constraint}
% This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
{\color{black}
% Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks.
% Both experience and DAG framework manuals (e.g., Hadoop and Spark) recommend that multi-round execution of each stage will benefit the performance of applications.
As discussed in the observation in Subsection \ref{observation}, it is common to have multi-round execution of each stage. 
If one of the tasks in a round missed a memory cache, the re-fetch overhead will become a bottleneck and then slow down the whole stage. 
% If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 
% PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously. 
% Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least.
}
Therefore, SCache master sets blocks of one round as the minimum unit of storage management.
We refer to this as the all-or-nothing constraint.
% According to all-or-nothing constraint, SCache master leverages the pre-scheduled results to determine the bound of each round, and sets blocks of one round as the minimum unit of storage management.
% For those incomplete units, SCache marks them as the lowest priority.

@@

{\color{black}
\subsection{Discussion of Fault Tolerance}\label{fault}
% how to handle faults? -> maybe replication -> tradeoff
For now, SCache only restarts failed workers without recovering their data.
SCache leaves the fault handling to the DAG frameworks.
If a failure happens in a SCache worker during shuffle phases, the $getBlock$ API will return a data not found error which causes the DAG framework restarts the current stage.
During the re-computing, the DAG frameworks still use SCache to gain shuffle optimization.
A possible way to avoid this re-computing is to use replications to recover the data.
However, such replications can introduce a significant network overhead.
We believe that the current way is more promising because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as the paralleled recovery of Spark. 
% Meanwhile, SCache can still provide shuffle optimization during the re-computing.
}

### 2019-09-14 scache/tii/tex/model.tex
Remove blue words

\subsection{The FRQ Model}\label{model_overview}
% The current distributed computing frameworks mostly use DAGs to describe the computation logic. 
% A shuffle phase is required between each adjacent DAG computation phases.
{\color{blue}
We propose the FRQ model to better analyze the relationship between the computation phase and the shuffle phase in the DAG computing.
% The FRQ model focuses on describing the overhead caused by the shuffle process.
The FRQ model focuses on describing the shuffle overhead which significantly effected by the scheduling strategy.
% This overhead does not only depends on the input data size, computation speed, complexity of algorithms, and other parameters but also on which scheduling strategy the job takes.
% By using the FRQ model, we can analyze the advantages of each strategy in various situations.
After quantifying computing and I/O resources, we use the FRQ model to evaluate different resource scheduling strategies.
% For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.

@@

% The FRQ model uses these overlaps to describe different scheduling strategies.
{\color{blue}
Besides, the FRQ model also needs to input the scheduling strategies the framework takes.
The FRQ model needs to know the start time of each phases.
For example, as shown in Figure \ref{fig:model_hadoop}, this strategy starts the shuffle phase and the reduce phase at the same time.
And Figure \ref{fig:model_basic} shows the pre-fetching strategy used by SCache. In the pre-fetching strategy, the shuffle phase starts as soon as it can in the map phase.
}

@@

{\color{blue}
\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and (\(K \times T_{P\_Shuffle}\)) represents the computing overhead.
\(T_{P\_Shuffle}\) represents the overlap time between the shuffle phase and the reduce phase as shown in Figure \ref{fig:model_basic}. \(T_{Shuffle}\) represents the total time of the shuffle phase. 
% The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks. This relationship will be shown in the following Subsection \ref{model_analysis}.  
\(K\) is an empirical value which represents the overhead caused by shuffle waiting. 
Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation needs to wait for the transfer results. This waiting causes the overhead.

>>>>

\subsection{The FRQ Model}\label{model_overview}
% The current distributed computing frameworks mostly use DAGs to describe the computation logic. 
% A shuffle phase is required between each adjacent DAG computation phases.
{\color{black}
We propose the FRQ model to better analyze the relationship between the computation phase and the shuffle phase in the DAG computing.
% The FRQ model focuses on describing the overhead caused by the shuffle process.
The FRQ model focuses on describing the shuffle overhead which significantly effected by the scheduling strategy.
% This overhead does not only depends on the input data size, computation speed, complexity of algorithms, and other parameters but also on which scheduling strategy the job takes.
% By using the FRQ model, we can analyze the advantages of each strategy in various situations.
After quantifying computing and I/O resources, we use the FRQ model to evaluate different resource scheduling strategies.
% For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.

@@

% The FRQ model uses these overlaps to describe different scheduling strategies.
{\color{black}
Besides, the FRQ model also needs to input the scheduling strategies the framework takes.
The FRQ model needs to know the start time of each phases.
For example, as shown in Figure \ref{fig:model_hadoop}, this strategy starts the shuffle phase and the reduce phase at the same time.
And Figure \ref{fig:model_basic} shows the pre-fetching strategy used by SCache. In the pre-fetching strategy, the shuffle phase starts as soon as it can in the map phase.
}

@@

{\color{black}
\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and (\(K \times T_{P\_Shuffle}\)) represents the computing overhead.
\(T_{P\_Shuffle}\) represents the overlap time between the shuffle phase and the reduce phase as shown in Figure \ref{fig:model_basic}. \(T_{Shuffle}\) represents the total time of the shuffle phase. 
% The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks. This relationship will be shown in the following Subsection \ref{model_analysis}.  
\(K\) is an empirical value which represents the overhead caused by shuffle waiting. 
Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation needs to wait for the transfer results. This waiting causes the overhead.

### 2019-09-14 scache/tii/tex/optimization.tex
Remove blue words

\section{Shuffle Optimization}
\label{opt}
This section presents detailed methodologies to achieve shuffle optimization. 
{\color{blue}
Firstly, we discuss the reason causes shuffle overhead in the DAG frameworks.
In the following subsection, we propose a shuffle data management system to decouple shuffle from execution. 
And we propose the pre-scheduling and pre-fetching to hide shuffle overhead in multi-round map tasks.
Furthermore, two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}) are used to improve the accuracy of prediction in the pre-scheduling.
}

@@

{\color{blue}
\subsection{Observations}\label{observation}
% DAG - shuffle - couple \& dependency - overhead in job - formula - how to optimize? - decouple \& pre-fetch - memory

@@

\subsection{Decouple Shuffle from Execution}
{\color{blue}
To decouple the shuffle from reduce tasks, we propose a shuffle data management system called SCache to take over all shuffle data from the DAG frameworks.
SCache provides two APIs named $putBlock$ and $getBlock$ to manage the shuffle data.
On the map side, after shuffle data blocks are produced, the map task uses $putBlock$ to transfer the data blocks to SCache.
%  instead of keeping them on local storage.
Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks to SCache's reserved memory and release the slot immediately.
After getting the shuffle data, SCache starts to shuffling data immediately.
% SCache gets the shuffle data as soon as the end of a map task's execution and starts to shuffling data immediately.
% SCache leverages the property of multi-round tasks to 
On the reduce side, due to the shuffle data pre-fetching of SCache, the reduce task use $getBlock$ to get the shuffle data from SCache.

@@

% \subsection{Pre-scheduling with Application Context}
{\color{blue}
\subsection{Pre-scheduling and Pre-fetching Shuffle Data}
% multi-round -> how to optimize? -> pre-schedule -> pre-fetch -> formula
The pre-scheduling and pre-fetching are the most critical aspects of the optimization.
% Multi-round tasks execution is used to gain better parallelism in most of DAG frameworks. For example, Spark recommends 2-3 tasks per CPU core in tasks configuration.
% Since shuffle data is available as soon as the map task finished, and the network is idle in map phases, 
SCache starts pre-fetching and hides shuffle overhead into multi-round map tasks.
However, the shuffle data cannot be pre-fetched without the awareness of task-node mapping.

@@

% \subsubsection{Random Mapping Problem}\label{randomassign}
% {\color{blue}
% % Mapping tasks to nodes randomly and evenly is the simplest pre-scheduling way.
% To evaluate the performance of scheduling strategies, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
% We run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
% The performance of random mapping drops as the round number grows. 
% This is because the data skew commonly exists in data-parallel computing \cite{skewtune}. 
% Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
% In addition, randomly mapping also ignores the data locality between shuffle map output and reduce input, which may introduce extra network traffic in the cluster.
% }
% The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
% We use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% The average shuffle read time is $3.2\%$ of total reduce completion time.
% We remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
% As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
% The performance of random mapping drops as the round number grows. 
% Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
% This is because that data skew commonly exists in data-parallel computing \cite{skewtune}. 
% Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
% In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.

@@

{\color{blue}

@@

\subsubsection{Heuristic MinHeap Scheduling}\label{h-minheap}
% As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
% But ignoring the data locality can introduce extra network transfer. 
% In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap Scheduling algorithm (Algorithm \ref{hminheap}).
To balance load while minimizing the network traffic, we present the \textit{Heuristic MinHeap Scheduling} algorithm (Algorithm \ref{hminheap}).
{\color{blue}
% For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum. 
To keep the pre-scheduling load balance, we maintain a min-heap in the first $while$ loop (i.e., line 6-11).
We use the min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
Spark FIFO only can achieve $2\text{-}approximation$ optimum.
}
% Since the sizes of tasks are considered while scheduling, \textit{Heuristic MinHeap Scheduling} can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
% Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.
Since the algorithm only maintains a min-heap and traverses $reduce$ for swapping, the algorithm needs $O(n)$ operations.

{\color{blue}
To evaluate \textit{Heuristic MinHeap Scheduling} algorithm, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
As shown in Figure \ref{fig:sim}, we run the simulation under three scheduling schemes: Random Mapping, Spark FIFO, and heuristic MinHeap.
After balancing load based on the job context (e.g. shuffle size, data locality), \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than Spark (average 2.7\%) and Random Mapping.
%  (becomes negative after the round one).
}

>>>>

\section{Shuffle Optimization}
\label{opt}
This section presents detailed methodologies to achieve shuffle optimization. 
{\color{black}
Firstly, we discuss the reason causes shuffle overhead in the DAG frameworks.
In the following subsection, we propose a shuffle data management system to decouple shuffle from execution. 
And we propose the pre-scheduling and pre-fetching to hide shuffle overhead in multi-round map tasks.
Furthermore, two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}) are used to improve the accuracy of prediction in the pre-scheduling.
}

@@

{\color{black}
\subsection{Observations}\label{observation}
% DAG - shuffle - couple \& dependency - overhead in job - formula - how to optimize? - decouple \& pre-fetch - memory

@@

\subsection{Decouple Shuffle from Execution}
{\color{black}
To decouple the shuffle from reduce tasks, we propose a shuffle data management system called SCache to take over all shuffle data from the DAG frameworks.
SCache provides two APIs named $putBlock$ and $getBlock$ to manage the shuffle data.
On the map side, after shuffle data blocks are produced, the map task uses $putBlock$ to transfer the data blocks to SCache.
%  instead of keeping them on local storage.
Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks to SCache's reserved memory and release the slot immediately.
After getting the shuffle data, SCache starts to shuffling data immediately.
% SCache gets the shuffle data as soon as the end of a map task's execution and starts to shuffling data immediately.
% SCache leverages the property of multi-round tasks to 
On the reduce side, due to the shuffle data pre-fetching of SCache, the reduce task use $getBlock$ to get the shuffle data from SCache.

@@

% \subsection{Pre-scheduling with Application Context}
{\color{black}
\subsection{Pre-scheduling and Pre-fetching Shuffle Data}
% multi-round -> how to optimize? -> pre-schedule -> pre-fetch -> formula
The pre-scheduling and pre-fetching are the most critical aspects of the optimization.
% Multi-round tasks execution is used to gain better parallelism in most of DAG frameworks. For example, Spark recommends 2-3 tasks per CPU core in tasks configuration.
% Since shuffle data is available as soon as the map task finished, and the network is idle in map phases, 
SCache starts pre-fetching and hides shuffle overhead into multi-round map tasks.
However, the shuffle data cannot be pre-fetched without the awareness of task-node mapping.

@@

% \subsubsection{Random Mapping Problem}\label{randomassign}
% {\color{black}
% % Mapping tasks to nodes randomly and evenly is the simplest pre-scheduling way.
% To evaluate the performance of scheduling strategies, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
% We run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
% The performance of random mapping drops as the round number grows. 
% This is because the data skew commonly exists in data-parallel computing \cite{skewtune}. 
% Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
% In addition, randomly mapping also ignores the data locality between shuffle map output and reduce input, which may introduce extra network traffic in the cluster.
% }
% The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
% We use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% The average shuffle read time is $3.2\%$ of total reduce completion time.
% We remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
% As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
% The performance of random mapping drops as the round number grows. 
% Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
% This is because that data skew commonly exists in data-parallel computing \cite{skewtune}. 
% Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
% In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.

@@

{\color{black}

@@

\subsubsection{Heuristic MinHeap Scheduling}\label{h-minheap}
% As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
% But ignoring the data locality can introduce extra network transfer. 
% In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap Scheduling algorithm (Algorithm \ref{hminheap}).
To balance load while minimizing the network traffic, we present the \textit{Heuristic MinHeap Scheduling} algorithm (Algorithm \ref{hminheap}).
{\color{black}
% For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum. 
To keep the pre-scheduling load balance, we maintain a min-heap in the first $while$ loop (i.e., line 6-11).
We use the min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
Spark FIFO only can achieve $2\text{-}approximation$ optimum.
}
% Since the sizes of tasks are considered while scheduling, \textit{Heuristic MinHeap Scheduling} can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
% Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.
Since the algorithm only maintains a min-heap and traverses $reduce$ for swapping, the algorithm needs $O(n)$ operations.

{\color{black}
To evaluate \textit{Heuristic MinHeap Scheduling} algorithm, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
As shown in Figure \ref{fig:sim}, we run the simulation under three scheduling schemes: Random Mapping, Spark FIFO, and heuristic MinHeap.
After balancing load based on the job context (e.g. shuffle size, data locality), \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than Spark (average 2.7\%) and Random Mapping.
%  (becomes negative after the round one).
}
